Modelling the emergence of whisker barrels

### 2020-06-30 paper/briefpaper/brief.tex
Updates to sensitivity analysis paras

% Blue changes are major point 2 (competition mechanism) and other, general
% uncategorised changes.
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
% Red for Stuart's first updates
\newcommand{\stu}[1]{\textcolor{red}{#1}}
% Minor point 4:
\newcommand{\mpfour}[1]{\textcolor{revgreen}{#1}}
% Minor point 6:
\newcommand{\mpsix}[1]{\textcolor{revpurp}{#1}}
% Justify competition:
\newcommand{\justifycomp}[1]{\textcolor{revpurp2}{#1}}
% Justify gamma/interaction parameter choice
\newcommand{\justifygammas}[1]{\textcolor{revpink}{#1}}
% Describe the metrics
\newcommand{\metrics}[1]{\textcolor{revred}{#1}}
% Parameter search. Major point 3
\newcommand{\paramsearch}[1]{\textcolor{revbblack}{#1}}
% Sensitivity analysis. Major point 3
\newcommand{\sensitivity}[1]{\textcolor{revgblack}{#1}}

@@

% Justify competition term. This pulled from Stuart's Google doc
\justifycomp{We reasoned that an arbitrary number of distinct field locations
  may be specified using a minimum of two guidance fields, if the tendency for
  the density of each projection to concentrate is appropriately balanced
  against the tendency of projections that interact more strongly with the
  guidance fields to migrate further in the directions specified by their
  gradients. Accordingly, projections that interact most strongly with a given
  guidance gradient would come to occupy cortical locations at which that
  field has extreme values, leaving adjacent locations available to be
  occupied by projections with the next strongest interactions, and so
  forth. This would in principle allow the \emph{relative} locations of the
  fields to be specified by the relative values of the interaction parameters,
  $\gamma$, and hence for a topological map in the cortex to be specified by a
  spatial ordering of the $\gamma$ values at the level of the thalamus.}

\justifycomp{Such dynamics are quite unlike those described by classic
  chemospecificity models} \citep{sperry_chemoaffinity_1963},
\justifycomp{which essentially assume center-points by specifying conditions
  in the target tissue that instruct pre-identified afferents to stop
  growing. Consider, for example, that when simulated in isolation from
  one-another, all projections in the model described would simply migrate to
  the extrema of the cortical guidance fields.}

\justifycomp{Testing this reasoning required increasing the strength of the
  competition between simulated thalamocortical projections for cortical
  territory, by increasing the tendency for the density of each projection to
  concentrate. The major modification required was thus to introduce into the
  model an additional source of competition between thalamic projections.}
%
The term in parentheses in Eq.\,\ref{eq:dc} represents competition between
thalamocortical projections for a limited availability of cortical
connections. To introduce competition also in terms of axon branching,
\cmnt{whilst ensuring that $a_i$ is conserved over time,} we
redefined
%
\begin{equation} \label{eq:comp}
  \color{blue}
  \chi_i(\mb{x}, t) = \frac{\epsilon a_i}{N-1} \nabla \textstyle\sum_{j\ne i}^{N}{a_j}.
  \color{black}
\end{equation}
%
\justifycomp{This term contributes to the \emph{flux} of axonal branching as
  an additional source of diffusion, which reduces the branching density for a
  given projection where the branches of other projections are dense. The
  strength of this additional competition is parameterized by
  $\epsilon$}. Note that this operation is local to individual afferent
projections.

\justifygammas{In addition, the model outlined requires that molecular
  guidance gradients in the cortex are complemented by graded values of the
  interaction strengths, $\gamma$, at the level of the thalamus. While the
  precise mechanisms by thalamic and cortical gradients interact during
  development have not been fully characterised, the presence of complementary
  thalamic and cortical molecular guidance gradients has been well established
  experimentally. In particular, the EphA4 receptor and its ligand ephrin-A5
  are distributed in complementary gradients in the somatosensory thalamus and
  cortex} (\citealp{vanderhaeghen_mapping_2000,miller_epha7-ephrin-a5_2006}).
\justifygammas{Cells originating in the medial part of ventrobasal thalamus
  (comprising VPM and VPL) express high levels of EphA receptors and project
  to the lateral part of S1, which expresses low levels of ephrin-A5, and
  cells originating in the lateral part of ventrobasal thalamus express low
  levels of EphA receptors and project to the medial part of S1, which
  expresses high levels of ephrin-A5} (see
\citealp{gao_regulation_1998,dufour_area_2003,vanderhaeghen_developmental_2004,speer_grading_2005,torii_role_2013}).

\justifygammas{For simplicity, both the thalamic interaction gradients and the
  cortical guidance fields in the model were chosen in the first instance to
  be linear and orthogonal. Hence a given pair of gamma values corresponds to
  the coordinate of a barreloid center in the VPM (in a reference plane
  defined by the anterior-posterior and medial-lateral axes. Coordinates were
  estimated from Fig 5d of} \citep{haidarliu_size_2001}, \justifygammas{and
  scaled (arbitrarily) such that $\gamma\in\pm 2$.}

A cortical boundary enclosing \cmnt{the} 41 \cmnt{macrovibrissae} barrels was
traced from a cytochrome oxidase stain from \cite{zheng_signal_2001}
\cmnt{(using original data kindly supplied by the authors)}, and
Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved for $N=41$ projections on the
resulting domain, using $M=2$ linear signalling gradients aligned with the
anterior-posterior and medial-lateral axes.  \mpfour{These gradients may
  extend well beyond the boundary of the barrel field (e.g. as ephrin-5 does;
  see \citealp{miller_epha7-ephrin-a5_2006}, their Fig.\,11) but they are
  shown within the barrel fields boundary in Fig.\,\ref{fig:main}A to aid the
  visualization. Simulations were iterated through 30000 iterations of
  Eqs.\,\ref{eq:dc}--\ref{eq:comp} ($\delta t=0.0001$)}

@@

% New section to describe and introduce the metrics
\metrics{First, we used an algorithm introduced by Honda to measure the
  discrepancy of each barrel shape from a Dirichletform shape. Low
  overall values of the \emph{Honda-}$\delta$ metric obtained from simulated
  barrels indicate a close correspondence of the simulated barrel field with a
  Voronoi tesselation, and thus with a biological barrel field. For the
  % Run ./build/sim/honda boundaries/rat_barrels/wb_110405_Dirichlet.svg to
  % get this result:
  tesselation overlaid on the real barrel field in Fig.\,1A, $\delta=0.025$,
  and a reduction in the Honda-$\delta$ metric in simulation
  confirmed that an equivalent `good' Voronoi pattern} (see
    \citealp{senft_mouse_1991}) \metrics{emerged within $\approx$~20000
  iterations (Fig.\,\ref{fig:main}D, red squares). Second, we devised a
  \emph{pattern difference} measure that is sensitive to deviations in the
  component shapes and overall topographic registration of two tesselations,
  $\eta$, and we used this measure to compare the simulated barrel fields to
  the real barrel field from which the simulation boundary shape was obtained
  (see Materials and Methods for details). A similar reduction in pattern
  difference over simulation time confirmed that the shapes and arrangement of
  emergent connection fields matched those of the real barrel field by around
  20000 iterations. Third, we measured the \emph{connection selectivity} at
  each location on the cortical sheet, as the connection density of the most
  dense projection divided by the sum over all projection densities, $\omega$.}

\metrics{Against these three metrics we are also able to characterise the
  robustness of self-organization to the model parameters, and to investigate
  the sensitivity of the model to variation in its inputs.}

@@

% Full page width
\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig3.png}
    \caption{
      \sensitivity{\textbf{A} Sensitivity of the system pattern
        metrics $\delta(t)$ (top row), $\omega(t)$ (middle row) and $\eta(t)$
        (bottom row), evaluated at $t=30000$ steps,
        to three classes of perturbation. $y$-axes and colour scales have identical ranges
        to the colour scales in Fig.\,\ref{fig:paramsweep}, to ease comparison
        with the parameter exploration.
        %
        \emph{Column 1:} Random noise drawn from a uniform distribution,
        $(\gamma_{max}-\gamma_{min})\,U(0,\nu_\gamma)$, added
        to the values for the interaction parameters, $\gamma_{i,j}$ used in
        Fig.\,\ref{fig:main}.
        %
        \emph{Column 2:} Random noise $(\rho_{max} - \rho_{min})\,U(0, \nu_{\rho})$
        was added to each hex element of $\rho_1(\mb{x})$ and $\rho_2(\mb{x})$ and the result
        was smoothed by convolution with a symmetric 2D
        Gaussian kernel of width $\sigma_\rho$. Colour maps in this column
        thus show the effect of changing the magnitude and the length scale of
        noise in the guidance fields.
        %
        \emph{Column 3:} Colour maps show the result of setting the rotational angle
        of the linearly varying guidance field, $\rho_1(\mb{x})$, to $\phi_{\rho_1}$,
        and modifying its overall gain to $G_{\rho_1}$, whilst keeping the
        parameters of $\rho_2(\mb{x})$
        unchanged from those used in the simulation in
        Fig.\,\ref{fig:main}, for which $\phi_{\rho_1}=6$\textdegree~and
        $\phi_{\rho_2}=84$\textdegree.
        %
        \textbf{B} Four ways in which the perturbations in \textbf{A} affect
        the patterns. i) The effect of significant interaction parameter noise
        causes barrels to become swapped from the positions they would
        otherwise take. ii) High magnitude, short lengthscale noise in
        $\rho(\mb{x})$ leads to `wiggly' boundaries between barrels. iii)
        Shows the effect of reducing the slope of $\rho_1$ (by a factor of 10)
        which reduces the strength of the axons' interaction with the guidance
        field in the left-right sense. Barrel rows B, C and D become `crushed'
        down the center line, and edge barrels dominate. iv) The effect of
        rotating $\rho_1$ by 20\textdegree~is a relatively mild distortion of
        the pattern in the anticlockwise sense.
      }
    }
    \label{fig:sens}
  \end{fullwidth}
\end{figure}

% This section needs to emphasize that the absolute values of gamma are not important
\sensitivity{We performed a sensitivity analysis to determine if the quality of the
  pattern was affected by perturbations to any of the following inputs:
%
  i)~the magnitude and offset of the noise applied to $a_i$ at $t=0$;
%
  ii)~random noise applied to the interaction parameters, $\gamma_{i,j}$;
%
  iii)~random noise (at various length scales) applied to the guidance fields;
%
  and
%
  iv)~The angle and magnitude of one of the guidance fields, ($\rho_1$;
  Fig.\,\ref{fig:main}A).
%
  In the following analysis, we always evaluated the three pattern metrics,
  $\delta$ (the Honda Voronoi metric), $\eta$ (the pattern-match metric) and
  $\omega$ (which measures selectivity of connections, $c_i$) after running
  the model for 30000 simulation steps.}

\sensitivity{First, we conducted 10 runs of the simulation shown in
  Fig.\,\ref{fig:main}C to evaluate the mean and standard deviation of the
  three metrics in the default model. The
  results (where deviations occur as a result of the different random initial
  conditions for $a_i$) were $\delta=0.089\,(0.004)$, $\eta=0.2108\,(0.002)$ and
  $\omega=0.2165\,(0.0001)$. None of the three metrics were strongly affected
  by the random changes to $a_i$ on each run. The results give a baseline from
  which to evaluate whether changes in the other inputs have a statistically
  significant effect.}

\sensitivity{Next, we modified the parameters of the generating uniform distribution
  to initialize $a_i$ for each hex to $0.1+{U}(0,0.4)$ (increasing the variability of
  $a_i(\mb{x},t=0)$ without changing the mean initial activation). We ran this
  system 10 times and obtained the results $\delta=0.090\,(0.005)$,
  $\eta=0.2136\,(0.004)$ and $\omega=0.2166\,(0.0003)$. Paired two-sample t-tests
  demonstrated that the increase in noise amplitude made no significant
  difference to the metric results ($\delta:
  \mathrm{t}=-0.69,\mathrm{p}=0.49$,
  $\eta: \mathrm{t}=-2.0,\mathrm{p}=0.06$,
  $\omega: \mathrm{t}=-1.7,\mathrm{p}=0.11$). 10 runs of a
  noise-free initial condition with $a_i=0.3$ for every hex showed that
  the model is deterministic (all runs produced the results $\delta=0.0928$,
  $\eta=0.21236$ and $\omega=0.21649$) and that stochasticity in
  $a_i(\mb{x},t=0)$ is not required by this model, as all three results lay within
  one standard deviation of those for the runs in which $a_i$ was initialized stochastically.}

@@

\sensitivity{Fig\,\ref{fig:sens}A shows the results for perturbations ii) to iv). The
  first column shows the results for the three metrics where the interaction
  parameters $\gamma_{i,j}$ are replaced by $\gamma_{i,j}'$ according to
  $\gamma_{i,j}' = \gamma_{i,j} + U(0,4\nu_\gamma)$, where $\nu_\gamma$ is the
  chosen magnitude of the noise (the proportion of the full range of
  $\gamma_{i,j}$, which is 4). The Voronoi nature of the pattern ($\delta$)
  and the selectivity of the fields are not strongly affected by interaction
  parameter noise, but the pattern metric, $\eta$ shows a... ADD SUB GRAPH.}

@@

>>>>

% Blue changes are major point 2 (competition mechanism) and other, general
% uncategorised changes.
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
% Red for Stuart's first updates
\newcommand{\stu}[1]{\textcolor{red}{#1}}
% Minor point 4:
\newcommand{\mpfour}[1]{\textcolor{revgreen}{#1}}
% Minor point 6:
\newcommand{\mpsix}[1]{\textcolor{revpurp}{#1}}
% Justify competition:
\newcommand{\mpfive}[1]{\textcolor{revpurp2}{#1}}
% Justify gamma/interaction parameter choice. major point 1.
\newcommand{\MPone}[1]{\textcolor{revpink}{#1}}
% Describe the metrics
\newcommand{\metrics}[1]{\textcolor{revred}{#1}}
% Parameter search. Major point 3
\newcommand{\paramsearch}[1]{\textcolor{revbblack}{#1}}
% Sensitivity analysis. Major point 3
\newcommand{\sensitivity}[1]{\textcolor{revgblack}{#1}}

@@

% Justify competition term. This pulled from Stuart's Google doc
\mpfive{We reasoned that an arbitrary number of distinct field locations
  may be specified using a minimum of two guidance fields, if the tendency for
  the density of each projection to concentrate is appropriately balanced
  against the tendency of projections that interact more strongly with the
  guidance fields to migrate further in the directions specified by their
  gradients. Accordingly, projections that interact most strongly with a given
  guidance gradient would come to occupy cortical locations at which that
  field has extreme values, leaving adjacent locations available to be
  occupied by projections with the next strongest interactions, and so
  forth. This would in principle allow the \emph{relative} locations of the
  fields to be specified by the relative values of the interaction parameters,
  $\gamma$, and hence for a topological map in the cortex to be specified by a
  spatial ordering of the $\gamma$ values at the level of the thalamus.}

\mpfive{Such dynamics are quite unlike those described by classic
  chemospecificity models} \citep{sperry_chemoaffinity_1963},
\mpfive{which essentially assume center-points by specifying conditions
  in the target tissue that instruct pre-identified afferents to stop
  growing. Consider, for example, that when simulated in isolation from
  one-another, all projections in the model described would simply migrate to
  the extrema of the cortical guidance fields.}

\mpfive{Testing this reasoning required increasing the strength of the
  competition between simulated thalamocortical projections for cortical
  territory, by increasing the tendency for the density of each projection to
  concentrate. The major modification required was thus to introduce into the
  model an additional source of competition between thalamic projections.}
%
The term in parentheses in Eq.\,\ref{eq:dc} represents competition between
thalamocortical projections for a limited availability of cortical
connections. To introduce competition also in terms of axon branching,
\cmnt{whilst ensuring that $a_i$ is conserved over time,} we
redefined
%
\begin{equation} \label{eq:comp}
  \color{blue}
  \chi_i(\mb{x}, t) = \frac{\epsilon a_i}{N-1} \nabla \textstyle\sum_{j\ne i}^{N}{a_j}.
  \color{black}
\end{equation}
%
\mpfive{This term contributes to the \emph{flux} of axonal branching as
  an additional source of diffusion, which reduces the branching density for a
  given projection where the branches of other projections are dense. The
  strength of this additional competition is parameterized by
  $\epsilon$}. Note that this operation is local to individual afferent
projections.

\MPone{In addition, the model outlined requires that molecular
  guidance gradients in the cortex are complemented by graded values of the
  interaction strengths, $\gamma$, at the level of the thalamus. While the
  precise mechanisms by which thalamic and cortical gradients interact during
  development have not been fully characterised, the presence of complementary
  thalamic and cortical molecular guidance gradients has been well established
  experimentally. In particular, the EphA4 receptor and its ligand ephrin-A5
  are distributed in complementary gradients in the somatosensory thalamus and
  cortex} (\citealp{vanderhaeghen_mapping_2000,miller_epha7-ephrin-a5_2006}).
\MPone{Cells originating in the medial part of ventrobasal thalamus
  (comprising VPM and VPL) express high levels of EphA receptors and project
  to the lateral part of S1, which expresses low levels of ephrin-A5, and
  cells originating in the lateral part of ventrobasal thalamus express low
  levels of EphA receptors and project to the medial part of S1, which
  expresses high levels of ephrin-A5} (see
\citealp{gao_regulation_1998,dufour_area_2003,vanderhaeghen_developmental_2004,speer_grading_2005,torii_role_2013}).

\MPone{For simplicity, both the thalamic interaction gradients and the
  cortical guidance fields in the model were chosen in the first instance to
  be linear and orthogonal. Hence a given pair of gamma values corresponds to
  the coordinate of a barreloid center in the VPM (in a reference plane
  defined by the anterior-posterior and medial-lateral axes. Coordinates were
  estimated from Fig 5d of} \citep{haidarliu_size_2001}, \MPone{and
  scaled (arbitrarily) such that $\gamma\in\pm 2$.}

A cortical boundary enclosing \cmnt{the} 41 \cmnt{macrovibrissae} barrels was
traced from a cytochrome oxidase stain from \cite{zheng_signal_2001}
\cmnt{(using original data kindly supplied by the authors)}, and
Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved for $N=41$ projections on the
resulting domain, using $M=2$ linear signalling gradients aligned with the
anterior-posterior and medial-lateral axes.  \mpfour{These gradients may
  extend well beyond the boundary of the barrel field (e.g. as ephrin-5 does;
  see \citealp{miller_epha7-ephrin-a5_2006}) but they are shown only within
  the boundary in Fig.\,\ref{fig:main}A, to indicate that external values are
  not used by the simulation. Simulations were stepped through 30000
  iterations of Eqs.\,\ref{eq:dc}--\ref{eq:comp} ($\delta t=0.0001$)}

@@

% New section to describe and introduce the metrics
\metrics{First, we used an algorithm introduced by Honda to measure the
  discrepancy of each barrel shape from a Dirichletform shape. Low
  overall values of the \emph{Honda-}$\delta$ metric obtained from simulated
  barrels indicate a close correspondence of the simulated barrel field with a
  Voronoi tesselation, and thus with a biological barrel field. For the
  % Run ./build/sim/honda boundaries/rat_barrels/wb_110405_Dirichlet.svg to
  % get this result:
  tesselation overlaid on the real barrel field in Fig.\,1A, $\delta=0.025$,
  and a reduction in the Honda-$\delta$ metric in simulation
  confirmed that an equivalent `good' Voronoi pattern} (see
    \citealp{senft_mouse_1991}) \metrics{emerged within $\approx$~20000
  iterations (Fig.\,\ref{fig:main}D, red circles). Second, we devised a
  \emph{pattern difference} measure that is sensitive to deviations in the
  component shapes and overall topographic registration of two tesselations,
  $\eta$, and we used this measure to compare the simulated barrel fields to
  the real barrel field from which the simulation boundary shape was obtained
  (see Materials and Methods for details). A similar reduction in pattern
  difference over simulation time confirmed that the shapes and arrangement of
  emergent connection fields matched those of the real barrel field by around
  20000 iterations. Third, we measured the \emph{connection selectivity} at
  each location on the cortical sheet, as the connection density of the most
  dense projection divided by the sum over all projection densities, $\omega$.}
%
\metrics{Against these three metrics we are also able to characterise the
  robustness of self-organization to the model parameters, and to investigate
  the sensitivity of the model to variation in its inputs.}

@@

% Full page width
\begin{figure}
  \begin{fullwidth}
    \includegraphics[width=\linewidth]{./Fig3.png}
    \caption{
      \sensitivity{\textbf{A} Sensitivity of the system pattern
        metrics $\delta(t)$ (top row), $\omega(t)$ (middle row) and $\eta(t)$
        (bottom row), evaluated at $t=30000$ steps,
        to three classes of perturbation. $y$-axes and colour scales have identical ranges
        to the colour scales in Fig.\,\ref{fig:paramsweep}, to ease comparison
        with the parameter exploration.
        %
        \emph{Column 1:} Random noise drawn from a uniform distribution,
        $(\gamma_{max}-\gamma_{min})\,U(0,\nu_\gamma)$, added
        to the values for the interaction parameters, $\gamma_{i,j}$ used in
        Fig.\,\ref{fig:main}.
        %
        \emph{Column 2:} Random noise $(\rho_{max} - \rho_{min})\,U(0, \nu_{\rho})$
        was added to each hex element of $\rho_1(\mb{x})$ and $\rho_2(\mb{x})$ and the result
        was smoothed by convolution with a symmetric 2D
        Gaussian kernel of width $\sigma_\rho$. Colour maps in this column
        thus show the effect of changing the magnitude and the length scale of
        noise in the guidance fields.
        %
        \emph{Column 3:} Colour maps show the result of setting the rotational angle
        of the linearly varying guidance field, $\rho_1(\mb{x})$, to $\phi_{\rho_1}$,
        and modifying its overall gain to $G_{\rho_1}$, whilst keeping the
        parameters of $\rho_2(\mb{x})$
        unchanged from those used in the simulation in
        Fig.\,\ref{fig:main}, for which
        $\phi_{\rho_2}=84$\textdegree and $G_{\rho_2}=1$.
        %
        \textbf{B} Four ways in which the perturbations in \textbf{A} affect
        the patterns. i) The effect of significant interaction parameter noise
        causes barrels to become swapped from the positions they would
        otherwise take. ii) High magnitude, short lengthscale noise in
        $\rho(\mb{x})$ leads to `wiggly' boundaries between barrels. iii)
        Shows the effect of reducing the slope of $\rho_1$ (by a factor of 10)
        which reduces the strength of the axons' interaction with the guidance
        field in the left-right sense. Barrel rows B, C and D become `crushed'
        down the center line, and edge barrels dominate. iv) The effect of
        rotating $\rho_1$ by 20\textdegree~is a relatively mild distortion of
        the pattern in the anticlockwise sense.
      }
    }
    \label{fig:sens}
  \end{fullwidth}
\end{figure}

% This section needs to emphasize that the absolute values of gamma are not important
\sensitivity{We performed a sensitivity analysis to determine if the quality
  of the pattern (i.e.~the values of $\delta$, $\eta$ \& $\omega$ after
  $t=30000$ steps) was affected by perturbations to any of the following
  inputs:
%
  i)~the magnitude and offset of the noise applied to $a_i$ at $t=0$;
%
  ii)~random noise applied to the interaction parameters, $\gamma_{i,j}$;
%
  iii)~random noise (at various length scales) applied to the guidance fields;
%
  and
%
  iv)~The angle and magnitude of one of the guidance fields, ($\rho_1$;
  Fig.\,\ref{fig:main}A).
}

\sensitivity{First, we conducted 10 runs of the simulation shown in
  Fig.\,\ref{fig:main}C to evaluate the mean and standard deviation of the
  metrics in the default model. The results (where deviations occur as a
  result of the different random initial conditions for $a_i$) were
  $\delta=0.089\,(0.004)$, $\eta=0.2108\,(0.002)$ and
  $\omega=0.2165\,(0.0001)$. The pattern was barely affected by the random
  changes to $a_i(t=0)$ on each run.}
%
\sensitivity{Next, we modified the parameters of the generating uniform
  distribution to initialize $a_i$ for each hex to $0.1+{U}(0,0.4)$,
  increasing the variability of $a_i(\mb{x},t=0)$ without changing the mean
  initial activation. We ran this system 10 times and obtained the results
  $\delta=0.090\,(0.005)$, $\eta=0.2136\,(0.004)$ and
  $\omega=0.2166\,(0.0003)$. Paired two-sample t-tests demonstrated that the
  increase in noise amplitude made no significant difference to the metric
  results ($\delta: \mathrm{t}=-0.69,\mathrm{p}=0.49$, $\eta:
  \mathrm{t}=-2.0,\mathrm{p}=0.06$, $\omega:
  \mathrm{t}=-1.7,\mathrm{p}=0.11$). 10 runs of a noise-free initial condition
  with $a_i=0.3$ for every hex showed that the model is deterministic (all
  runs produced the results $\delta=0.0928$, $\eta=0.21236$ and
  $\omega=0.21649$) and that stochasticity in $a_i(\mb{x},t=0)$ is not
  required by this model, as all three results lay within one standard
  deviation of those for the runs in which $a_i$ was initialized
  stochastically.}

@@

\sensitivity{Fig\,\ref{fig:sens}A shows the results for perturbations ii) to
  iv). The results show that the Voronoi nature of the pattern ($\delta$) and
  the selectivity of the fields are not strongly affected by interaction
  parameter noise, but the pattern metric, $\eta$ shows a degradation in the
  pattern arrangement when a) noise in the interaction parameters causes their
  disordering (find better way to express?), b) noise in the guidance field
  with a high magnitude and short length scale causes disruption to the barrel
  edges and c) the guidance fields tend towards a non-orthogonal arrangement,
  or if one field becomes substantially stronger in its interaction with the
  thalamocortical projections. Fig\,\ref{fig:sens}B shows perturbed examples.}

@@

Add paragraph on whisker trimming here.
